---
title: "Shiny App Project"
author: "Jerin Timothy James"
date: "`r Sys.Date()`"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny App Projecct

This is an R Markdown presentation to pitch my Shiny App for plot manipulations.

- The Shiny App is hosted on shinyapps.io
- The code is in my public GitHub
- This presentation includes the app demo

This Shiny App allows a user to select a number of data points and choice of plot display desired, scatterplot or bar chart.

First select the type of plot from the dropdown menu, then selected the number of data points from the slider, then hit update plot. A plot will be generated. Plots can be changed wihtout the need for hitting th eupdate plot button again if desired.

## Shiny App for Plot Manipulation Demo

```{r, echo = FALSE}
library(shiny)
shinyApp(
  ui=fluidPage(
  titlePanel("Plot Manipulation Shiny App"),
  sidebarLayout(
    sidebarPanel(
      # Input widget: Select input with options
      selectInput("plotType", "Select a Plot Type:", 
                  choices = c("Scatterplot", "Barplot")),
      sliderInput("numPoints", "Number of Data Points:", min = 10, max = 100, value = 50),
      actionButton("updatePlot", "Update Plot")
    ),
    mainPanel(
      # Output: Plot
      plotOutput("outputPlot")
    )
  )
),
server=function(input, output) {
  # Create a reactive data frame to store the data for the plot
  data <- reactive({
    num_points <- input$numPoints
    if (input$plotType == "Scatterplot") {
      data <- data.frame(x = rnorm(num_points), y = rnorm(num_points))
    } else {
      data <- data.frame(category = LETTERS[1:num_points], value = runif(num_points))
    }
    data
  })

  # Render the plot based on user input
  output$outputPlot <- renderPlot({
    if (input$plotType == "Scatterplot") {
      plot(data()$x, data()$y, main = "Scatterplot", xlab = "X-axis", ylab = "Y-axis")
    } else {
      barplot(data()$value, names.arg = data()$category, main = "Barplot")
    }
  })
  
  # Add an observer to update the plot when the button is clicked
  observeEvent(input$updatePlot, {
    output$outputPlot <- renderPlot({
      if (input$plotType == "Scatterplot") {
        plot(data()$x, data()$y, main = "Scatterplot", xlab = "X-axis", ylab = "Y-axis")
      } else {
        barplot(data()$value, names.arg = data()$category, main = "Barplot")
      }
    })
  })
}
  
  
  
)
```

## Resources

- ShinyApps.io dashboard site: https://www.shinyapps.io/admin/#/application/10423985
- Deployed shinyapps.io URL: https://timjames1999.shinyapps.io/Plotchoice/
- GitHub public repo with ReadMe and code: https://github.com/timjames1999/ShinyAppProject



## Conclusion

I have met the project requirements of creating a Shiny App, deploying it, showing the code, and creating a presenation about it.
